Kindly Bent to Free Us

### 2019-07-05 kindly/motivation.tex
preserved linearity

\begin{lstlisting}
let uri = "postgresql://localhost:5432"

(* Create a database connection pool. *)
let pool = Pool.create (fun () -> Db.connect uri)

(* Use the pool in queries. *)
let create_user name =
  Pool.use &pool (fun connection ->
    Db.insert "users" [("name", name)] connection)
\end{lstlisting}
    \caption{Example of use}
    \label{ex:pool}
  \end{subfigure}~
  \begin{subfigure}[t]{.45\linewidth}
\begin{lstlisting}
type ('a:'k) pool : 'k = {
  spawn : unit -> 'a ;
  queue : 'a CQueue.t;
}

>>>>

\begin{lstlisting}
(* Using the pool in queries. *)
let create_user pool name =
  Pool.use &pool (fun connection ->
    Db.insert "users" [("name", name)] connection)

let uri = "postgresql://localhost:5432"
let main users =
  (* Create a database connection pool. *)
  let pool = Pool.create (fun _ -> Db.connect uri)
  List.parallel_iter (create_user &pool) users
  Pool.consume (fun c -> Db.close c)
\end{lstlisting}
    \caption{Example of use}
    \label{ex:pool}
  \end{subfigure}~
  \begin{subfigure}[t]{.45\linewidth}
\begin{lstlisting}
type ('a:'k) pool : 'k = {
  spawn : unit -> 'a ;
  queue : 'a CQueue.t;
}
